Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex
yufei

With the above fact, next we prove Lemma~\ref{lmm:hv:type1:recur-output} by resorting to the algorithm generate-$\J_2$ (see Section~\ref{sec:hv:type2}). For each tuple $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$, this algorithm adds $|\contained_{R_{k-2}}(\bm{t})|\geq 1$ tuples to $\J_2$. Therefore, $|\J(R_1,...,R_{k-3},H',V)| \le |\J_2| \le \out$, where the last inequality used the definition of $\J_2$; see \eqref{eqn:hv:type2:J2}.

>>>>

With the above fact, next we prove Lemma~\ref{lmm:hv:type2:recur-output} by resorting to the algorithm generate-$\J_2$ (see Section~\ref{sec:hv:type2}). For each tuple $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$, this algorithm adds $|\contained_{R_{k-2}}(\bm{t})|\geq 1$ tuples to $\J_2$. Therefore, $|\J(R_1,...,R_{k-3},H',V)| \le |\J_2| \le \out$, where the last inequality used the definition of $\J_2$; see \eqref{eqn:hv:type2:J2}.
